Paper Visualizations

### 2022-05-20 eda/paper-graphics.Rmd
started table2

```{r, results='asis'}
author_types <- amicus %>% select(chcauf, lifauo, medauf, medauo, legauf, legauo, relauf, relauo) %>%
  mutate(across(where(is.character), as.numeric)) %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) %>%
  pivot_longer(.,cols = c(chcauf, lifauo, medauf, medauo, legauf, legauo, relauf, relauo), names_to = "var", values_to = "ct") %>%
  arrange(var)

author_types <- author_types %>% mutate(author_type = substr(var, 1, 3), position = substr(var, 4, 6)) %>% select(-var)

@@

author_table <- author_types %>% pivot_wider(names_from = position, values_from = ct)
author_table[1,3] <- 0
author_table[3,2] <- 0

total <- c("Total", sum(author_table$`Reproductive Rights`), sum(author_table$`Antiabortion`))
author_table <- rbind(author_table, total)

stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.  Total Number of Amicus Briefs by Amicus Type in the Supreme Court Abortion Cases", notes = "a. Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).  Also, the same organizations file briefs in multiple cases.", header=FALSE, type = 'html', notes.align = 'l')
```

>>>>

```{r, results='asis'}
#transform dataframe
author_types <- amicus %>% select(chcauf, lifauo, medauf, medauo, legauf, legauo, relauf, relauo) %>%
  mutate(across(where(is.character), as.numeric)) %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) %>%
  pivot_longer(.,cols = c(chcauf, lifauo, medauf, medauo, legauf, legauo, relauf, relauo), names_to = "var", values_to = "ct") %>%
  arrange(var)

#clean up names
author_types <- author_types %>% mutate(author_type = substr(var, 1, 3), position = substr(var, 4, 6)) %>% select(-var)

@@

#clean values
author_table <- author_types %>% pivot_wider(names_from = position, values_from = ct)
author_table[1,3] <- 0
author_table[3,2] <- 0

#add totals
total <- c("Total", sum(author_table$`Reproductive Rights`), sum(author_table$`Antiabortion`))
author_table <- rbind(author_table, total)

#create table
stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.  Total Number of Amicus Briefs by Amicus Type in the Supreme Court Abortion Cases", notes = "a. Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).  Also, the same organizations file briefs in multiple cases.", header=FALSE, type = 'html', notes.align = 'l')
```

# Table 2

```{r, results='asis'}
#read in models
forg_privacy_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_privacy_interactions.rds")
forg_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/forg_undue_interactions.rds")
lif_undue_interactions <- readRDS("../modeling/justicemq-interactions/models/lif_undue_interactions.rds")

stargazer(forg_privacy_interactions, forg_undue_interactions, lif_undue_interactions, title="Results", type='html',align=TRUE)
```
